Type Refinements for the Working Class

### 2016-01-20 paper.tex
Spell out coinductive definition of approx
fix / clarify wording

An $\Sorts$-\emph{operator signature} is an $\Sorts$-arity-indexed family of copresheaves on
$\SCtx$, namely $\HypJ{\Of{\Operators_a}{\Sets^\SCtx}}{\IsArity{a}}$; this is
an intensional generalization of the state of affairs for standard universal
algebra, where operators are arity-indexed families of \emph{sets}. The point
of fibering over symbol contexts is to induce an open-ended indexing
mechanism for operators; the functorial liftings of $\SCtx$-morphisms
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
equip operators $\Member{\vartheta}{\Operators_a(\Upsilon)}$ with a suitable
renaming action $\Member{\Rename{\rho}{\vartheta}}{\Operators_a(\Upsilon')}$.%
%
\footnote{
  In~\cite{sterling-morrison:2015}, the authors defined operator signatures as
  \emph{sheaves} on $\OpCat{(\SCtx)}$ under the atomic topology (alternatively,
  pullback-preserving presheaves), where all non-empty sieves cover; the sheaf
  condition induces the unique existence of \emph{strengthenings} for
  operators. However, because we do not use strengthening in the present
  development, we have omitted this part of the apparatus for the sake of
  simplicity.
}
%
We call the pair $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ an \emph{abt signature}.

@@

\begin{definition}[Computational Approximation]
  Because $[-_\tau]$ is monotonic, it has a greatest fixed point, which we will
  call \emph{computational approximation},
  $\Of{\preccurlyeq_\tau}{\Hom{\SemU}{\mathbb{1}}{\Pow{\Exprs_\tau^2}}}$,
  written pointwise as $\PBinRel{\preccurlyeq_\tau}{\Upsilon}{M}{N}$.
\end{definition}

>>>>

An $\Sorts$-\emph{operator signature} is an $\Sorts$-arity-indexed family of copresheaves on
$\SCtx$, namely $\HypJ{\Of{\Operators_a}{\Sets^\SCtx}}{\IsArity{a}}$; this is
an intensional generalization of the state of affairs for standard universal
algebra, where the operators are an arity-indexed family of \emph{sets}. The point
of fibering over symbol contexts is to induce an open-ended indexing
mechanism for operators; the functorial liftings of $\SCtx$-morphisms
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
equip operators $\Member{\vartheta}{\Operators_a(\Upsilon)}$ with a suitable
renaming action $\Member{\Rename{\rho}{\vartheta}}{\Operators_a(\Upsilon')}$.%
%
\footnote{
  In~\cite{sterling-morrison:2015}, the authors defined operator signatures as
  \emph{sheaves} on $\OpCat{(\SCtx)}$ under the atomic topology (alternatively,
  pullback-preserving presheaves), where all non-empty sieves cover; the sheaf
  condition induces the unique existence of \emph{strengthenings} for
  operators. However, because we do not use strengthening in the present
  development, we have omitted this part of the apparatus for the sake of
  simplicity.
}
%
We call the pair $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ an \emph{abt signature}.

@@

\begin{definition}[Computational Approximation]
  Because $[-_\tau]$ is monotonic, it has a greatest fixed point, which we will
  call \emph{computational approximation},
  $\Of{\preccurlyeq_\tau}{\Hom{\SemU}{\mathbb{1}}{\Pow{\Exprs_\tau^2}}}$,
  written pointwise as $\PBinRel{\preccurlyeq_\tau}{\Upsilon}{M}{N}$.
  In other words:
  \[
    \infer{
      \PBinRel{\preccurlyeq_\tau}{\Upsilon}{M}{N}
    }{
      \forall
      \begin{tikzcd}[cramped, ampersand replacement = \&]
        \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
      \end{tikzcd}.\
      \land\left\{
        \begin{array}{l}
          \Eval{\Upsilon'}{\tau}{\Rename{\rho}{M}}{\App{\vartheta}{\vec{E}}}\\
          \IsCanOperator{\Upsilon'}{\vartheta}{\MkArity{\vec{v}}{\tau}}
        \end{array}
      \right\}
      \implies
      \land\left\{
        \begin{array}{l}
          \Eval{\Upsilon'}{\tau}{\Rename{\rho}{N}}{\App{\vartheta}{\Vec{F}}}\\
          \PBinRel{\preccurlyeq_{\vec{v}}}{\Upsilon'}{\vec{E}}{\vec{F}}
        \end{array}
      \right\}
    }
  \]
\end{definition}
